Home

### 2016-05-04 analysis/index.Rmd
add estimate_mode

## Optimization method: EM vs Interior Point
*  [Compare loglik achieved by EM vs Interior Point](checkIP.html)

@@

>>>>

## Optimization method: EM vs Interior Point
*  [Compare loglik achieved by EM vs Interior Point](checkIP.html)
*  [Compare speed of EM vs Interior Point](IPvsEM.html)

@@

## Check how estimating the mode performs

* [Basic check of non-zero model option](estimate_mode.html)
